Missing data: Current practice in football research and recommendations for improvement

### 2020-09-10 paper/paper.Rmd
change wording in simulation dataset section.

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting hamstring strain injury, using number of sprints and sprint distance as x-variables
# Add a sentence in the paper talking about this
# I'm stuck at the momement how to simulate the occurance of an injury (0,1), but with only low incidence of 1's in the dataset
# I'm also stuck how to simulate the number of sprints, but between say 50 and 200 sprints

>>>>

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting hamstring strain injury, using number of sprints and sprint distance as x-variables
# We need to add a sentence in the paper talking about this
# I'm stuck at the momement how to simulate the occurance of an injury (0,1), but with only low incidence of 1's in the dataset
# I'm also stuck how to simulate the number of sprints, but between say 50 and 200 sprints
